deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-05-07 paper.tex
bib tweak

\leavevmode\vadjust pre{\hypertarget{ref-optuna}{}}%
Akiba, Takuya, Shotaro Sano, Toshihiko Yanase, Takeru Ohta, and Masanori
Koyama. 2019. {``Optuna: A Next-Generation Hyperparameter Optimization
Framework.''} In \emph{Proceedings of the 25th ACM SIGKDD}, 2623--31.

@@

\leavevmode\vadjust pre{\hypertarget{ref-coppa}{}}%
---------. 1998. {``Children's Online Privacy Protection Act.''}

>>>>

\leavevmode\vadjust pre{\hypertarget{ref-optuna}{}}%
Akiba, Takuya, Shotaro Sano, Toshihiko Yanase, Takeru Ohta, and Masanori
Koyama. 2019. {``Optuna: A Next-Generation Hyperparameter Optimization
Framework.''} \emph{25th ACM SIGKDD}, 2623--31.

@@

\leavevmode\vadjust pre{\hypertarget{ref-coppa}{}}%
Legislature of the United State. 1998. {``Children's Online Privacy Protection Act.''}
